---
title: "RD design analysis"
author: "Xuyuan Zhang"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
geometry: "left=1.5cm,right=1.5cm,top=1cm,bottom=1.5cm"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(tidy=TRUE)
knitr::opts_chunk$set(fig.height=4)
knitr::opts_chunk$set(fig.width=7)
knitr::opts_chunk$set(warning=FALSE)
options(encoding = "UTF-8")
set.seed(123)
```

## structure

1. we first report the figure and export the figure to the folder named figures in directory
2. we then report the main result of the regressions
3. lastly, we report the placebo test and the robustness check

```{r}
# these are the packages that we need to import
library(dplyr)
library(haven)
library(rdd)
library(ggplot2)
library(rdrobust)
library(plm)
library(xtable)
library(pander) # this is for table showing
library(latex2exp) # this is to export it
setwd("E:/umich/RealEstateBrokerage-main")
# need to place data on the base directory
data <- read_dta("template.dta")
working_directory <-"E:/umich/RealEstateBrokerage"
```

```{r}
panel_data <- pdata.frame(data, index = c("id", "year"))
panel_data$L_jiadian <- lag(panel_data$jiadian, 1)
panel_data$L_kind <- lag(panel_data$kind, 1)
panel_data$L_hotel <- lag(panel_data$hotel, 1)
panel_data$L_shop_mall <- lag(panel_data$shop_mall, 1)
panel_data$L_museum <- lag(panel_data$museum, 1)
panel_data$L_old <- lag(panel_data$old, 1)
panel_data$L_ktv <- lag(panel_data$ktv, 1)
panel_data$L_mid <- lag(panel_data$mid, 1)
panel_data$L_prim <- lag(panel_data$prim, 1)
panel_data$L_west_food <- lag(panel_data$west_food, 1)
panel_data$L_super <- lag(panel_data$super, 1)
panel_data$L_sub <- lag(panel_data$sub, 1)
panel_data$L_park <- lag(panel_data$park, 1)
```

we use these control variables

```{r}
control_variables <- c(
  "jiadian", "kind", "hotel", "shop_mall", "museum", "old", "ktv", "mid", "prim", "west_food", "super", "sub", "park", 
  "area", "bedroom", "toilet", "house_age", "floor_level", "green_ratio", "total_building", "total_floor_number", "living_room", "elevator_ratio", "kitchen", "floor_ratio", "total_resident",
  "pm25", "pop", "light",
  "non_online_effect", "ln_negotiation_period", "ln_watch_time", "ln_nego_changes", "ln_lead", "ln_watch_people"
)
testing_variables <- c("ln_negotiation_period", "ln_watch_time", "ln_nego_changes", "ln_lead", "ln_watch_people", "ln_end_price")
```

```{r}
ci_level = 95
h = 0.066
cutoff = 0.41
running_var = panel_data$nearest_store_distances
running_var <- as.numeric(running_var)
filtered_data <- panel_data[abs(running_var - cutoff) <= h, ]

# Export the first RD plot to its own PDF file
pdf("RD_Plot_1st_Order.pdf", width = 8, height = 4) # Adjust the width and height as needed
rdplot(y = filtered_data$ln_income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 1,
       title = "RD-plot 1st order polynomial",
       x.label = "Nearest distance to Lianjia's stores",
       y.label = "Log of income in the community", col.dots = "blue")
dev.off() # Close the PDF device

# Export the second RD plot to its own PDF file
pdf("RD_Plot_2nd_Order.pdf", width = 8, height = 4) # Adjust the width and height as needed
rdplot(y = filtered_data$ln_income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 2,
       title = "RD-plot 1st order polynomial",
       x.label = "Nearest distance to Lianjia's stores",
       y.label = "Log of income in the community", col.dots = "blue")
dev.off() # Close the PDF device

# Export the third RD plot to its own PDF file
pdf("RD_Plot_3rd_Order.pdf", width = 8, height = 4) # Adjust the width and height as needed
rdplot(y = filtered_data$ln_income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 3,
       title = "RD-plot 3rd order polynomial",
       x.label = "Nearest distance to Lianjia's stores",
       y.label = "Log of income in the community", col.dots = "blue")
dev.off() # Close the PDF device
```

```{r}
bw_methods <- c("mserd", "cerrd")
kernel_list <- c("uniform", "triangular")
results_list <- list()
counter <- 1
for (bw_method in bw_methods) {
    for (kernel_in in kernel_list){
        result <- rdrobust(y = panel_data$ln_income, x = panel_data$nearest_store_distances, 
                     c = 0.41,
                     p = 1, 
                     bwselect = bw_method, kernel = kernel_in)
        
        effective_obs <- sum(result$N_h)

        results_list[[counter]] <- data.frame(
        Method = bw_method,
        Kernel = kernel_in,
        Estimate = format(result$coef[1], digits = 3, scientific = FALSE),
        SE = format(result$se[1], digits = 3, scientific = FALSE),
        Z = format(result$z[1], digits = 3, scientific = FALSE),
        PValue = format(result$pv[1], digits = 3, scientific = FALSE),
        Bandwidth = format(result$bws[1], digits = 3, scientific = FALSE),
        EffectiveObs = effective_obs
    )
        counter <- counter + 1
    }
}
results <- do.call(rbind, results_list)
latex_code <- print(xtable(results, 
                           caption = "RD Estimates with Different Bandwidth Selection Methods and Kernels", 
                           label = "tab:rd_bandwidth_kernel_results"), 
                    include.rownames = FALSE, 
                    type = "latex",
                    print.results = FALSE)
write(latex_code, file = paste(working_directory , "result_tables/rdd_result_summary.tex", sep='/'))
print(results)
```


# checkings:

1. Donut Hole: Exclude observations close to the cutoff and estimate the effect with the remaining data. If the discontinuity persists despite the absence of data around the cutoff, this provides evidence against a model misspecification.
2. Mccrary (2008) test: Conduct a McCrary density test to check if there is a discontinuity in the density of the running variable at the cutoff. A significant discontinuity may suggest manipulation or sorting around the cutoff.
3. Placebo test: If you have pre-treatment covariates, you can test whether these covariates also jump at the cutoff. If they do, this might suggest manipulation or a violation of the RD design assumptions. If they don’t, it strengthens the case for a true treatment effect.

## Donut Hole Test

```{r}
cutoff
donut_width <- 0.011
panel_data_donut <- panel_data[!(panel_data$nearest_store_distances >= (cutoff - donut_width) & 
                                 panel_data$nearest_store_distances <= (cutoff + donut_width)),]
result_donut <- rdrobust(y = panel_data_donut$ln_income, 
                         x = panel_data_donut$nearest_store_distances, 
                         c = cutoff,
                        p = 1, h = 0.066, b = 0.135)
pander(cbind(result_donut$coef, result_donut$pv))
print(result_donut)
```

```{r}
perform_rd_analysis <- function(cutoff, donut_width, h, b) {
  # select the data that we need
  panel_data_donut <- panel_data[!(panel_data$nearest_store_distances >= (cutoff - donut_width) & 
                                   panel_data$nearest_store_distances <= (cutoff + donut_width)),]
  # run the rdrobust result
  result_donut <- rdrobust(y = panel_data_donut$ln_income, 
                           x = panel_data_donut$nearest_store_distances, 
                           c = cutoff,
                           p = 1, h = h, b = b)
  # return the coefficient and the p value
  conventional <- c("Conventional", result_donut$coef[1, 1], result_donut$se[1, 1], result_donut$pv[1, 1])
  bias_corrected <- c("Bias-Corrected", result_donut$coef[2, 1], result_donut$se[2, 1], result_donut$pv[2, 1])
  robust <- c("Robust", 
              format(result_donut$coef[3, 1], digits = 3, scientific = FALSE), 
              format(result_donut$se[3, 1], digits = 3, scientific = FALSE), 
              format(result_donut$pv[3, 1], digits = 3, scientific = FALSE))
  
  # combine the results
  result_table <- rbind(conventional, bias_corrected, robust)
  colnames(result_table) <- c("Method", "Coef", "SE", "p-value")
  return(result_table)
}

cutoff = 0.41
donut_widths <- c(0.01, 0.0125, 0.015, 0.0175, 0.02, 0.0225, 0.025)
results <- list()

for (donut in donut_widths) {
  result <- perform_rd_analysis(cutoff, donut, 0.066, 0.135)
  results[[paste0("donut_", donut)]] <- result
}

```

```{r}
perform_rd_analysis <- function(cutoff, donut_width, h, b) {
  # select the data that we need
  panel_data_donut <- panel_data[!(panel_data$nearest_store_distances >= (cutoff - donut_width) & 
                                   panel_data$nearest_store_distances <= (cutoff + donut_width)),]
  # run the rdrobust result
  result_donut <- rdrobust(y = panel_data_donut$ln_income, 
                           x = panel_data_donut$nearest_store_distances, 
                           c = cutoff, covs = panel_data_donut[, control_variables],
                           p = 1, h = h, b = b)
  # return the coefficient and the p value
  conventional <- c("Conventional", result_donut$coef[1, 1], result_donut$se[1, 1], result_donut$pv[1, 1])
  bias_corrected <- c("Bias-Corrected", result_donut$coef[2, 1], result_donut$se[2, 1], result_donut$pv[2, 1])
  robust <- c("Robust", 
              format(result_donut$coef[3, 1], digits = 3, scientific = FALSE), 
              format(result_donut$se[3, 1], digits = 3, scientific = FALSE), 
              format(result_donut$pv[3, 1], digits = 3, scientific = FALSE))
  
  # combine the results
  result_table <- rbind(conventional, bias_corrected, robust)
  colnames(result_table) <- c("Method", "Coef", "SE", "p-value")
  return(result_table)
}

cutoff = 0.41
donut_widths <- c(0.01, 0.0125, 0.015, 0.0175, 0.02, 0.0225, 0.025)
results_with_control <- list()

for (donut in donut_widths) {
  result <- perform_rd_analysis(cutoff, donut, 0.066, 0.135)
  results_with_control[[paste0("donut_", donut)]] <- result
}
```

```{r}
# with controls
combined_results_with_control <- do.call(rbind, lapply(names(results_with_control), function(donut) {
  result <- results_with_control[[donut]]
  robust_result <- result[result[, "Method"] == "Robust", ]
  data.frame(Donut_Width = donut, Method = robust_result[1], Coef = robust_result[2], SE = robust_result[3], p_value = robust_result[4])
}))
colnames(combined_results_with_control) <- c("Donut Width", "Method", "Coef", "SE", "p-value")

# without controls
combined_results <- do.call(rbind, lapply(names(results), function(donut) {
  result <- results[[donut]]
  robust_result <- result[result[, "Method"] == "Robust", ]
  data.frame(Donut_Width = donut, Method = robust_result[1], Coef = robust_result[2], SE = robust_result[3], p_value = robust_result[4])
}))
colnames(combined_results) <- c("Donut Width", "Method", "Coef", "SE", "p-value")

merged_results <- merge(combined_results_with_control, combined_results, by = c("Donut Width", "Method"))
merged_results_df <- as.data.frame(merged_results)

colnames(merged_results_df) <- c("Donut Width", "Method", "Coef", "SE", "p-value", "Coef", "SE", "p-value")

# print as a latex table
latex_code <- print(xtable(merged_results_df, 
                           caption = "RD Analysis Donut RD Results with and without Controls", 
                           label = "tab:rd_robust_results"), 
                    include.rownames = FALSE, 
                    type = "latex",
                    print.results = FALSE)

latex_code <- gsub("\\\\begin\\{tabular\\}\\{llllllll\\}\n  \\\\hline\n", 
                   "\\\\begin{tabular}{llllllll}\n  \\\\hline\n &  & \\\\multicolumn{3}{c}{Without Control} & \\\\multicolumn{3}{c}{With Control} \\\\\\\\\n", 
                   latex_code)

latex_code <- gsub("\\\\end\\{tabular\\}", "\\\\end{tabular}\nNote that the cutoff is 0.41, the main bandwidth is 0.066 and the bias bandwidth is 0.135.", latex_code)

write(latex_code, file = paste(working_directory , "result_tables/donut_robust.tex", sep='/'))
```


## McCrary Sorting Test

```{r}
# Give it the running variable and the cutpoint
# it will automatically produce a plot and select the number of bins and the bandwidth
# The output will be the p-value for the presence of a discontinuity
DCdensity(filtered_data$nearest_store_distances, cutpoint = 0.41, bw = 0.066, verbose = TRUE, plot = FALSE)
DCdensity(panel_data$nearest_store_distances, cutpoint = 0.41, bw = 0.066, verbose = TRUE, plot = FALSE)
```

## PlaceBo Test

Conducting placebo test. We shall using the same validation bandwidth and bias correction bandwidth. The results are good overall

```{r}
testing_variables <- c("pop", "light", "price_concession", "ln_end_price", "ln_nego_changes", "ln_watch_time", "green_ratio", "bedroom", "ln_watch_people", "living_room", "ln_negotiation_period", "museum", "kind", "mid", "sub", "house_age", "total_building")

results_list <- list()

counter <- 1

for (validation in testing_variables) {
  rd_result <- rdrobust(y = panel_data[[validation]], x = panel_data$nearest_store_distances,
                        c = 0.41, h = 0.066, b = 0.135,
                        bwselect = "mserd", kernel = "triangular")
  
  # 提取有效观测值数量并相加
  effective_obs <- sum(rd_result$N_h)
  
  # 提取结果并存储到列表中
  results_list[[counter]] <- data.frame(
    Covariate = validation,
    Estimate = format(rd_result$coef[1], digits = 3, scientific = FALSE),
    SE = format(rd_result$se[1], digits = 3, scientific = FALSE),
    Z = format(rd_result$z[1], digits = 3, scientific = FALSE),
    PValue = format(rd_result$pv[1], digits = 3, scientific = FALSE),
    Bandwidth = format(rd_result$bws[1], digits = 3, scientific = FALSE),
    EffectiveObs = effective_obs
  )
  counter <- counter + 1
}

results <- do.call(rbind, results_list)

latex_code <- print(xtable(results, 
                           caption = "Placebo Test Results for Different Covariates", 
                           label = "tab:placebo_test_results"), 
                    include.rownames = FALSE, 
                    type = "latex",
                    print.results = FALSE)
write(latex_code, file = paste(working_directory , "result_tables/rdd_placebo_test.tex", sep='/'))
print(results)

```

## Cutoff Point movement

The movement of the cutoff point should make the estimation non-significant

```{r}
cutoffs_width <- c(0.15, 0.2, 0.25, 0.30, 0.35, 0.50, 0.65, 0.7)

results_list <- list()
counter <- 1
for (cutoff in cutoffs_width) {
  # rd_result <- rdrobust(y = panel_data$ln_income, x = panel_data$nearest_store_distances, c = cutoff, h = 0.066, b = 0.135, bwselect = "mserd", kernel = "triangular")
  rd_result <- rdrobust(y = panel_data$ln_income, x = panel_data$nearest_store_distances,
                        c = cutoff)
  
  # 提取有效观测值数量并相加
  effective_obs <- sum(rd_result$N_h)
  # 提取结果并存储到列表中
  results_list[[counter]] <- data.frame(
    Cutoff = cutoff,
    Estimate = format(rd_result$coef[1], digits = 3, scientific = FALSE),
    SE = format(rd_result$se[1], digits = 3, scientific = FALSE),
    Z = format(rd_result$z[1], digits = 3, scientific = FALSE),
    PValue = format(rd_result$pv[1], digits = 3, scientific = FALSE),
    Bandwidth = format(rd_result$bws[1], digits = 3, scientific = FALSE),
    EffectiveObs = effective_obs
  )
  counter <- counter + 1
}
results <- do.call(rbind, results_list)

latex_code <- print(xtable(results, 
                           caption = "Placebo Test Results for Different Cutoff Point", 
                           label = "tab:movement_cutoff"), 
                    include.rownames = FALSE, 
                    type = "latex",
                    print.results = FALSE)
write(latex_code, file = paste(working_directory , "result_tables/movement_cutoff.tex", sep='/'))
print(results)
```

